Supplementary Information: Tropical tree drought sensitivity is jointly shaped by drought characteristics, species adaptations, and individual microenvironments

### 2025-06-18 doc/supplementary_information.Rmd
updated SI figures and SI file

![**Figure S1:** Raw climate data timeseries from 2009 to 2020 from the Forest Fire Research Station near HKK. Measurements represent daily rolling means over a 30-day time window for precipitation, max temperature and VPD and rolling sum for number of dry days.](display/climvars_fullseries.png)

![**Figure S2:** Climate anomalies for all variables from 2009 to 2020from the Forest Fire Research Station near HKK. Values represent number of standard deviations from the long-term mean for daily rolling mean values.](display/climvars_anomalies_fullseries.png)

>>>>

![**Figure S1:** Raw climate data timeseries from 2009 to 2023 from ERA5Land and CHIRPS. Measurements represent daily rolling means over a 30-day time window for precipitation, max temperature and VPD and rolling sum for number of dry days.](display/climvars_fullseries_remote.png)

![**Figure S2:** Climate anomalies for all variables from 2009 to 2020. Values represent number of standard deviations from the long-term mean for daily rolling mean values.](display/climvars_anomalies_fullseries_remote.png)
